---
title: 'Final assessment part 3.2: comparison between Dutch and English speakers using the ASA Questionnaire'
author: "Johan Hensman"
date: "21 June, 2023"
output:
  pdf_document:
    includes:
      in_header: header.tex
    latex_engine: xelatex
    fig_caption: yes
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This document presents statistical analyses of the comparison between Chinese and Dutch speakers perception of ASAs using the ASA questionnaire as reported in the paper. 
Code based on Fengxiang Li with adaptations made to Dutch.


We use the following packages:
```{r, collapse=TRUE, results='hide', message=FALSE, warning=FALSE}

library(foreign) # Open various data files
library(nlme)    # Run multilevel linear models
library(car)     # Package linear regression
#install.packages("devtools")
#devtools::install_github("rmcelreath/rethinking")
library(rethinking) # Run ulam
library(haven) # Use read_sav fuction
library(dplyr) # Use select function
library(knitr) # Get markdown file
library(tinytex) # Use TeX environment
library(rticles) # Use CTeX documents template
library(pander) # For pandering tables
panderOptions("table.alignment.default","left")

```


# Data file 
## data_cultures.sav

In Transform_raw_data.Rmd in this folder, we transformed the the different data files into 1 bigger datafile, where the data is stored in the long format. For more details look into Transform_raw_data.Rmd or Transform_raw_data.pdf.

```{r, message=FALSE, warning=FALSE, echo=TRUE}

data_culture <- data.frame(read_sav("data_cultures.sav"))
```

# Analyses results reported in Section Results
## Comparison of Human-ASA Interaction between Different Cultural Backgrounds

The results were reported in the section results. The analysis was based on human-ASA interaction evaluation of 30 Dutch speaker and 30 Chinese speakers on ASIMO. We compared human-ASA interaction between these two cultural background populations mentioned above. Two-level linear regression model was implemented to explore construct and dimension score differences between two sample groups. For the Bayesian analysis we used the rethinking package developed by Richard McElreath^[https://www.rdocumentation.org/packages/rethinking/versions/2.13].

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide', error=FALSE} 

cul_list <- data.frame(ConstructID=double(),mean_Chi=double(),sd_Chi=double(), 
                       mean_Du=double(),sd_Du=double(),mean_diff=double(), 
                       sd_diff=double(),lo2_5=double(), 
                       hi97_5=double(),n_eff=double(),Rhat4=double(), 
                       P_posterior=double(),zero_excl=character())
#Initialize output list of Construct/dimension differences between two cultural
#groups

for(j in 1:24){
  print(j)
  d_c<-subset(data_culture, ConstructID==j, select=c(Culture, Rating))
  # select scores data for ASAQ construct j

  # Define the model we fit on the data. This is a multilevel model
  # with culture as fixed effect
  m <- ulam(
    alist(
      #Likelihood
      Rating ~ dnorm(mu, sigma),
      
      #Linear model
      mu <- a + c_cult*Culture,

      #Fixed priors
      a ~ dnorm(0, 2),
      c_cult ~ dnorm(0, 1), 
      sigma ~ dcauchy(0, 1)
    ), data = d_c, iter = 50000, chains = 4, cores = 4, log_lik = TRUE,
    control=list(adapt_delta=.99)
  )

  # Calculate posterior probability
  post_samples <- extract.samples(m, 1e4) 
  # Extract 10000 samples from the posterior distribution
  c_cult <- as.numeric(post_samples$c_cult)
  H0_post <- subset(c_cult, c_cult>0) 
  # Select samples with positive posterior values (positive bias)
  
  H0_post_p <- length(H0_post)/1e4    
  # Calculate probability of a positive bias
  H1_post_p <- 1 - H0_post_p          
  # Probability of a negative bias
  
  d_c_Chi <- subset(d_c, Culture == 0)
  # Subset of only Chinese mother tongue sample

  d_c_Du <- subset(d_c, Culture == 1)
  # Subset of only Dutch mother tongue sample 

  o <- precis(m,  depth=2, prob=.95)
  l <- data.frame(ConstructID = j,
                  mean_Du = mean(d_c_Du$Rating),
                  sd_Du = sd(d_c_Du$Rating),
                  mean_Chi = mean(d_c_Chi$Rating),
                  sd_Chi = sd(d_c_Chi$Rating),
                  mean_diff = as.numeric(o$mean[2]),
                  sd_diff = as.numeric(o$sd[2]),
                  lo2_5 = as.numeric(o$`2.5%`[2]), 
                  hi97_5 = as.numeric(o$`97.5%`[2]),
                  n_eff = as.numeric(o$n_eff[2]),
                  Rhat4 = as.numeric(o$Rhat4[2]),
                  P_posterior = max(H0_post_p,H1_post_p),
                  zero_excl = ifelse((as.numeric(o$`2.5%`[2])>0)
                                | (as.numeric(o$`97.5%`[2])<0),
                                '*','')
                  )
  # Line 2 in the precis output, are the results related to c_cul coefficient
  cul_list <- rbind(cul_list, l)
  # Store results in a list to print later on

}
```

The last step is the print the results of the model analysis.

```{r, echo=TRUE, message=FALSE, warning=FALSE, error=FALSE}

# Print results
cul_list$Construct=c('HLA','HLB','NA','NB','AAS','AU','PF','AL','AS','APP',
'UAA','AE','UE','UT','UAL','AA','AC','AI','AT','SP','IIS','AEI','UEP','UAI')
# Add construct/dimension name code
pander(select(cul_list,ConstructID,mean_Du,sd_Du,mean_Chi,sd_Chi,Construct), 
       caption="Construct/dimension differences between two cultural groups (Part 1)")
pander(select(cul_list,ConstructID,mean_diff,sd_diff,lo2_5,hi97_5,Construct), 
       caption="Construct/dimension differences between two cultural groups (Part 2)")
pander(select(cul_list,ConstructID,n_eff,Rhat4,P_posterior,zero_excl,Construct), 
       caption="Construct/dimension differences between two cultural groups (Part 3)")

# Print grand means
Variable <- c("mean_Du","sd_Du","mean_Chi","sd_Chi","mean_diff","sd_diff",
              "minimum_diff","maximum_diff","n_zero_excl","percent_zero_excl")
Grand_mean <- c(mean(cul_list$mean_Du),mean(cul_list$sd_Du),
                mean(cul_list$mean_Chi),mean(cul_list$sd_Chi),
                mean(abs(cul_list$mean_diff)),mean(cul_list$sd_diff),
                min(cul_list$mean_diff),max(cul_list$mean_diff),
                sum(cul_list$zero_excl=="*"),round(sum(cul_list$zero_excl=="*")
                /length(cul_list$ConstructID),digits=4)*100)
GrandMean <- cbind(Variable, Grand_mean)
# Calculate grand mean of mean_Chi, sd_Chi, mean_Eng, sd_Eng 
# sd_diff, grand mean of the absolute value of mean differences, number of 
# constructs/dimensions with credible bias indication, 
# and percentage of these constructs/dimensions
pander(GrandMean, caption = "Grand mean of 24 constructs/dimensions between two cultural groups")

```
