---
title: 'Final assessment part 1: Correlation between the orginal English and the newly translated Dutch ASA Questionnaire'
author: "Johan Hensman"
date: "21 June, 2023"
output:
  pdf_document:
    includes:
      in_header: header.tex
    latex_engine: xelatex
    fig_caption: yes
    number_sections: yes
    toc: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction

This document presents statistical analyses of correlation between English and Dutch ASA questionnaires for item level, construct/dimension level, and short versions of the ASA questionnaire as reported in the paper 
Code based on Fengxiang Li with adaptations made to Dutch.



We use the following packages:

```{r, collapse=TRUE, results='hide', message=FALSE, warning=FALSE}
library(foreign) # Open various data files
library(nlme)    # Run multilevel linear models
library(car)     # Package linear regression
library(haven) # Use read_sav fuction
library(dplyr) # Use select function
library(knitr) # Get markdown file
library(tinytex) # Use TeX environment
library(pander) # For pandering tables
panderOptions("table.alignment.default","left")
```

# Data files
The input data for this analysis is based on 3 files. These aren't the fully raw data collected on Qualtrics as it pre-processed to anonymize and delte columns that are not needed/allowed to publish. 

## Final_ASA_Dutch_Round_1_First_Half_anonym.sav"
The first survey was split in two to prevent fatigue. In the first group first 12 constructs were asked and the second group the last 12 constructs. The participants rated 44 and 46 questionnaire items each and 14 attention checks that all had to be correct. The participants had the option to not recommend their data, but this was of importance when creating the questionnaire. In this final assessment all data will be used. this file contains data of the first 12 constructs

## Final_ASA_Dutch_Round_1_Second_Half_anonym.sav
this file contains data from the last 12 constructs

## Final_ASA_Dutch_Round_2_anonym.sav
After the first round was performed 37 items needed to be retranslated as they had a low correlation value. We received 37 new translation as well as 27 alternative translations that needed to be evaluated. The results of that survey is saved in this file.
```{r, message=FALSE, warning=FALSE, echo=TRUE}
dataset <- read_sav("Final_ASA_Dutch_Round_1_First_Half_anonym.sav")
dataset2 <- read_sav("Final_ASA_Dutch_Round_1_Second_Half_anonym.sav")
dataset3 <- read_sav("Final_ASA_Dutch_Round_2_anonym.sav")
#Importing data
#"dataset" contains ASA question items from the first 12 constructs
#"dataset2" contains ASA question items from the last 12 constructs
```


The data has some columns that are not necessary for this analysis, so we only select the attention checks and the questionnaire items of the survey.
```{r, message=FALSE, warning=FALSE, echo=TRUE}
dataset <- data.frame(select(dataset, AC_English_1:Q_ITEMS_438.0))
dataset2 <- data.frame(select(dataset2, AC_English_1:Q42_442))
dataset3 <- data.frame(select(dataset3, AC_Dutch_1:English_UAI3))
#Selecting only relevant question items, which include attention checks 
#and ASA questionnaire items
```

Here, we change the column names of such that the ASA questionnaire items are renamed according to which language they are in, and which construct they belong to. In the Legend Q1.txt you can find the questions that they belonged to.
```{r, message=FALSE, warning=FALSE, echo=TRUE}
#Here, all the column names are changed so that ASA questionnaire items are 
#named according to their construct.
colnames(dataset)[59:102] <- c("D_HLA1", "D_HLA2", "D_HLA3", "D_HLA4", "D_HLB1",
                               "D_HLB2", "D_HLB3", "D_HLB4", "D_HLB5", "D_NA1", 
                               "D_NA2", "D_NA3", "D_NA4", "D_NA5", "D_NB1", 
                               "D_NB2", "D_NB3", "D_AAS1", "D_AAS2", "D_AAS3",
                               "D_AU1", "D_AU2", "D_AU3", "D_PF1", "D_PF2", 
                               "D_PF3", "D_AL1", "D_AL2", "D_R_AL3", "D_AL4", 
                               "D_AL5", "D_AS1", "D_AS2", "D_AS3", "D_APP1", 
                               "D_R_APP2", "D_APP3", "D_UAA1", "D_UAA2", 
                               "D_R_UAA3", "D_R_AE1", "D_AE2", "D_AE3", 
                               "D_R_AE4")
#Changing columns of Dutch ASA question items in dataset

colnames(dataset2)[61:106] <- c("D_UE1", "D_UE2", "D_UE3", "D_UT1", "D_UT2", 
                                "D_UT3", "D_UAL1", "D_UAL2", "D_UAL3", "D_UAL4", 
                                "D_UAL5", "D_UAL6", "D_AA1", "D_AA2", "D_AA3", 
                                "D_R_AC1", "D_R_AC2", "D_R_AC3", "D_R_AC4", 
                                "D_AI1", "D_AI2", "D_R_AI3", "D_AI4", "D_AT1", 
                                "D_AT2", "D_R_AT3", "D_SP1", "D_SP2", "D_SP3", 
                                "D_IIS1", "D_IIS2", "D_IIS3", "D_IIS4", 
                                "D_AEI1", "D_AEI2", "D_R_AEI3", "D_AEI4", 
                                "D_R_AEI5", "D_UEP1", "D_UEP2", "D_UEP3", 
                                "D_UEP4", "D_UAI1", "D_UAI2", "D_UAI3", 
                                "D_UAI4")
#Changing columns of Dutch ASA question items in dataset2

colnames(dataset)[8:51] <- c("HLA1", "HLA2", "HLA3", "HLA4", "HLB1", "HLB2", 
                             "HLB3", "HLB4", "HLB5", "NA1", "NA2", "NA3", "NA4", 
                             "NA5", "NB1", "NB2", "NB3", "AAS1", "AAS2", "AAS3", 
                             "AU1", "AU2", "AU3", "PF1", "PF2", "PF3", "AL1", 
                             "AL2", "R_AL3", "AL4", "AL5", "AS1", "AS2", "AS3", 
                             "APP1", "R_APP2", "APP3", "UAA1", "UAA2", "R_UAA3", 
                             "R_AE1", "AE2", "AE3", "R_AE4")
#Changing columns of English ASA question items in dataset

colnames(dataset2)[8:53] <- c("UE1", "UE2", "UE3", "UT1", "UT2", "UT3", "UAL1", 
                              "UAL2", "UAL3", "UAL4", "UAL5", "UAL6", "AA1", 
                              "AA2", "AA3", "R_AC1", "R_AC2", "R_AC3", "R_AC4", 
                              "AI1", "AI2", "R_AI3", "AI4", "AT1", "AT2", 
                              "R_AT3", "SP1", "SP2", "SP3", "IIS1", "IIS2", 
                              "IIS3", "IIS4", "AEI1", "AEI2", "R_AEI3", "AEI4", 
                              "R_AEI5", "UEP1", "UEP2", "UEP3", "UEP4", "UAI1", 
                              "UAI2", "UAI3", "UAI4")
#Changing columns of English ASA question items in dataset2
```

As the data got imported from Qualtrics not all cells had numeric values. So, we remove all text from the cells and make the text numerical. 
```{r, message=FALSE, warning=TRUE, echo=TRUE}
dataset <- as.data.frame(lapply(dataset[1:102], 
                              function(y) as.numeric(gsub('[a-zA-Z]', '', y))))
dataset2 <- as.data.frame(lapply(dataset2[1:106], 
                              function(y) as.numeric(gsub('[a-zA-Z]', '', y))))
dataset3 <- as.data.frame(lapply(dataset3[1:115], 
                              function(y) as.numeric(gsub('[a-zA-Z]', '', y))))
#Transform the data to numeric representation
```


In this section we can omit the attention checks and only keep the quuestionnaire items.
```{r, message=FALSE, warning=FALSE, echo=TRUE}
d1 <- as.data.frame(select(dataset, HLA1:R_AE4, D_HLA1:D_R_AE4))
# Select scores of 44 English items and corresponding Dutch translations
d2 <- as.data.frame(select(dataset2, UE1:UAI4, D_UE1:D_UAI4))
# Select scores of 46 English items and corresponding Dutch translations
d3 <- as.data.frame(select(dataset3, English_HLA1:English_UAI3, Dutch_HLA:Dutch_UAI3))
# Select scores of 37 English items and corresponding Dutch translations
```

We manually checked which translation had the highest ICC value and picked them to create the variable with the best values. The chosen translations and their corresponding ICC value can be found in the same folder of this codebase under Best_ICC_and_translations.xlsx. To confirm these values we calculate the ICC values again from the datafiles. So we combine the necessary columns from each dataset.

```{r, message=FALSE, warning=FALSE, echo=TRUE}
d_total1 <- cbind(select(d1,HLA1), select(d3,English_HLA1), 
                 select(d1,HLA3:HLB3), select(d3,English_HLB2),
                 select(d1,HLB5:NA1), select(d3,English_NA1:English_NB1), 
                 select(d1, NB2),  select(d3, English_NB3), select(d1, AAS1), 
                 select(d3, English_AAS1:English_AAS2), select(d1, AU1:AU2), 
                 select(d3, English_AU1), select(d1, PF1:PF3),
                 select(d3, English_AL1), select(d1, AL2:AL5), 
                 select(d3, English_AS1), select(d1, AS2), 
                 select(d3, English_AS2), select(d1,APP1:R_UAA3), 
                 select(d3,English_AE1:English_AE2), select(d1, AE3:R_AE4), 
                 select(d2, UE1), select(d3,English_UE1), select(d2, UE3:UT1), 
                 select(d3, English_UT1), select(d2, UT3:UAL1), 
                 select(d3, English_UAL1), select(d2, UAL3:AA2), 
                 select(d3, English_AA2), select(d2, R_AC1:AI4), 
                 select(d3, English_AT1), select(d2, AT2:R_AT3), 
                 select(d3, English_SP1), select(d2, SP2:SP3), 
                 select(d3, English_IIS1: English_AEI1), 
                 select(d2, AEI2:R_AEI5), 
                 select(d3, English_UEP), select(d2, UEP2:UAI1), 
                 select(d3, English_UAI1: English_UAI3))
#select all English items from their correspoding datasets.


d_total2 <- cbind(select(d1,D_HLA1), select(d3,Dutch_HLA), 
                 select(d1,D_HLA3:D_HLB3), select(d3,Dutch_HLB2), 
                 select(d1,D_HLB5:D_NA1), select(d3,Dutch_NA1), 
                 select(d3,Dutch_NA2_Alt1), select(d3,Dutch_NA3), 
                 select(d3,Dutch_NA4_Alt2:Dutch_NB1),select(d1, D_NB2), 
                 select(d3,Dutch_NB3_Alt2) , select(d1, D_AAS1),  
                 select(d3, Dutch_AAS1), select(d3, Dutch_AAS2_Alt4), 
                 select(d1, D_AU1:D_AU2), select(d3, Dutch_AU1_Alt1), 
                 select(d1, D_PF1:D_PF3), select(d3, Dutch_AL1_Alt1), 
                 select(d1, D_AL2: D_AL5), select(d3, Dutch_AS1_Alt1), 
                 select(d1, D_AS2), select(d3, Dutch_AS2_Alt3), 
                 select(d1,D_APP1:D_R_UAA3), select(d3, Dutch_AE1_Alt1), 
                 select(d3, Dutch_AE2), select(d1, D_AE3:D_R_AE4), 
                 select(d2, D_UE1), select(d3, Dutch_UE1_Alt2), 
                 select(d2, D_UE3:D_UT1), select(d3, Dutch_UT1_Alt1), 
                 select(d2, D_UT3:D_UAL1), select(d3, Dutch_UAL1_Alt1), 
                 select(d2, D_UAL3:D_AA2), select(d3, Dutch_AA2), 
                 select(d2, D_R_AC1:D_AI4), select(d3, Dutch_AT1_Alt1), 
                 select(d2, D_AT2:D_R_AT3), select(d3, Dutch_SP), 
                 select(d2, D_SP2:D_SP3), select(d3, Dutch_IIS1_Alt2), 
                 select(d3, Dutch_IIS2_Alt2), select(d3, Dutch_IIS3_Alt2), 
                 select(d3, Dutch_IIS4: Dutch_AEI1_Alt1), 
                 select(d2, D_AEI2:D_R_AEI5), select(d3, Dutch_UEP1_Alt1), 
                 select(d2, D_UEP2:D_UAI1), 
                 select(d3, Dutch_UAI1: Dutch_UAI3))
#select all Dutch items from their correspoding datasets.

d_total_Item <- cbind(d_total1, d_total2)
# Combine evaluation scores of the best items across the 3 data files.

```


As the columns of the 2nd round didnt had the proper naming, we renamed all columns again. (most values contained xx_xx_Alt 1 as there were multiple translation, but we want only the proper tags in the end.)
```{r, message=TRUE, warning=TRUE, echo=TRUE}
colnames(d_total_Item)[1:180] <- c("HLA1", "HLA2", "HLA3", "HLA4", "HLB1", "HLB2", 
                             "HLB3", "HLB4", "HLB5", "NA1", "NA2", "NA3", "NA4", 
                             "NA5", "NB1", "NB2", "NB3", "AAS1", "AAS2", "AAS3", 
                             "AU1", "AU2", "AU3", "PF1", "PF2", "PF3", "AL1", 
                             "AL2", "R_AL3", "AL4", "AL5", "AS1", "AS2", "AS3", 
                             "APP1", "R_APP2", "APP3", "UAA1", "UAA2", "R_UAA3", 
                             "R_AE1", "AE2", "AE3", "R_AE4","UE1", "UE2", "UE3", 
                             "UT1", "UT2", "UT3", "UAL1", "UAL2", "UAL3",
                             "UAL4", "UAL5", "UAL6", "AA1", "AA2", "AA3", 
                             "R_AC1", "R_AC2", "R_AC3", "R_AC4", "AI1", "AI2", 
                             "R_AI3", "AI4", "AT1", "AT2", "R_AT3", "SP1", 
                             "SP2", "SP3", "IIS1", "IIS2", "IIS3", "IIS4", 
                             "AEI1", "AEI2", "R_AEI3", "AEI4", "R_AEI5", "UEP1",
                             "UEP2", "UEP3", "UEP4", "UAI1", "UAI2", "UAI3",
                             "UAI4", "D_HLA1", "D_HLA2", "D_HLA3", "D_HLA4", 
                             "D_HLB1", "D_HLB2", "D_HLB3", "D_HLB4", "D_HLB5",
                             "D_NA1", "D_NA2", "D_NA3", "D_NA4", "D_NA5",
                             "D_NB1", "D_NB2", "D_NB3", "D_AAS1", "D_AAS2",
                             "D_AAS3", "D_AU1", "D_AU2", "D_AU3", "D_PF1", 
                             "D_PF2","D_PF3", "D_AL1", "D_AL2", "D_R_AL3",
                             "D_AL4", "D_AL5", "D_AS1", "D_AS2", "D_AS3",
                             "D_APP1", "D_R_APP2", "D_APP3", "D_UAA1",
                             "D_UAA2", "D_R_UAA3", "D_R_AE1", "D_AE2", "D_AE3", 
                             "D_R_AE4", "D_UE1", "D_UE2", "D_UE3", "D_UT1", 
                             "D_UT2", "D_UT3", "D_UAL1", "D_UAL2", "D_UAL3", 
                             "D_UAL4", "D_UAL5", "D_UAL6", "D_AA1", "D_AA2", 
                             "D_AA3", "D_R_AC1", "D_R_AC2", "D_R_AC3", 
                             "D_R_AC4", "D_AI1", "D_AI2", "D_R_AI3", "D_AI4", 
                             "D_AT1", "D_AT2", "D_R_AT3", "D_SP1", "D_SP2", 
                             "D_SP3", "D_IIS1", "D_IIS2", "D_IIS3", "D_IIS4",
                             "D_AEI1", "D_AEI2", "D_R_AEI3", "D_AEI4", 
                             "D_R_AEI5", "D_UEP1", "D_UEP2", "D_UEP3", 
                             "D_UEP4", "D_UAI1", "D_UAI2", "D_UAI3", "D_UAI4")
```

we already prepare also the data we need for the construct level. As construct level icc is only valid if all questions from 1 construct are answered by the same person, we had to take almost all values from the First dataset(which was split in two). There was one construct where all questions were asked in round 2 and resulted in a higher ICC value. So the construct level data contains 1 construct (with the tag IIS) from Round 2 and the rest originate from round 1. The necessary columns were renamed to show the correct tags.

```{r, message=FALSE, warning=FALSE, echo=TRUE}
d_total1 <- cbind(select(d1,HLA1:R_AE4), select(d2,UE1:SP3), 
                  select(d3, English_IIS1: English_IIS4), select(d2, AEI1:UAI4))
#select all English items from their correspoding datasets.

d_total2 <- cbind(select(d1,D_HLA1:D_R_AE4), select(d2,D_UE1:D_SP3), 
                  select(d3, Dutch_IIS1_Alt2), select(d3, Dutch_IIS2_Alt2), 
                  select(d3, Dutch_IIS3_Alt2), select(d3, Dutch_IIS4),
                  select(d2, D_AEI1:D_UAI4))
#select all Dutch items from their correspoding datasets.

d_total_Construct <- cbind(d_total1, d_total2)
#combine the items into 1.

colnames(d_total_Construct)[74:77] <- c("IIS1", "IIS2", "IIS3", "IIS4")
colnames(d_total_Construct)[164:167] <-c("D_IIS1", "D_IIS2", "D_IIS3", "D_IIS4")
# rename the necessary columns.

```


All scores that have an R_ in front have to be reversed. This was not necessary for the item-level ICC value, but it is for the construct level as questions like 'I don't like [the agent]' and 'I like [the agent]' will have opposite values so questions like 'i don't like [the agent]' are reversed.

```{r, message=TRUE, warning=TRUE, echo=TRUE}
for (i in grep("R_",colnames(d_total_Construct))){ 
# Find column number of reversing-scoring items and translations
  d_total_Construct[[i]][] <- d_total_Construct[[i]][]*(-1)
  # Reverse scores of reverse-scoring items and translations
}
```
# Analyses results reported in Section Results

## function/model for ICC calculation

We fit a multilevel model  with a fixed intercept (~1) and participants as the random intercept. $\rho_I =\frac{\tau^2}{\tau^2 + \sigma^2}$ is the formula needed to calculate the ICC where $\tau^2$ is the variance between participants, and $\sigma^2$ is the variance within the score of individual.

```{r, message=FALSE, warning=FALSE, echo=TRUE}
getICC <-function(model)
  # Function for ICC value calculation using multilevel linear model
{
  vc.model <- VarCorr(model)
  # Estimated variances and correlations between the random-effects terms
  sigma_var <-as.numeric(vc.model[2,1])
  # Variance within the groups
  tau_var <- as.numeric(vc.model[1,1])
  # Variance between the groups
  icc <- tau_var/(tau_var + sigma_var)
  # Calculate ICC value
  return(icc)
}
```

Next, we defined a function to run a multilevel mode. It takes as input the score from both languages and returns the ICC value.
```{r, message=FALSE, warning=FALSE, echo=TRUE}
getLME <-function(s_1,s_2)
  # Function for a linear mixed-effects model
{
  id<-rownames(s_2)
  # Row names that represent the ID number of each participant
  Score_Dutch<- data.frame(id, s_1, language= 1)
  # Transform Dutch scores from wide format to long format and label as 1
  Score_English<- data.frame(id, s_2, language= 2)
  # Transform English scores from wide format to long format and label as 2
  Score_total <- rbind(Score_Dutch, Score_English)
  # Combine Dutch and English scores in the long format 
  m0 <- lme(score ~ 1, data = Score_total, random = ~1|id, method = "ML")
  # Linear mixed-effects model with a fixed intercept and 
  # a random intercept of participant's ID number
  return(getICC(m0))
}
```

## ICC values for 90 items

Now the function and the data is prepared to calculate the ICC values for the 90 questionnaire items. The grand mean, standard deviation and the range is also presented Note: the first half contains all English data and the second half contains all Dutch data.
```{r, message=TRUE, warning=TRUE, echo=TRUE}

l_ICC <- data.frame(ItemID = double(), Item = character(), icc = double())
# Initialize output of ICC values of 44 items
n <- ncol(d_total_Item)

# Numbers of columns in d1
Dutch_column_offset <- ncol(d_total_Item)/2 
# Offset, the first column with scores of the Dutch version of ASAQ item
d0 <- data.frame(d_total_Item)


for (i in 1:90)
  # Go step by step to 90 items of the ASA questionnaire, whereby i is 
  #the ASA questionnaire item number
{
  score_Dutch <- na.omit(data.frame(score=d0[,i + Dutch_column_offset ])) 
  # Select scores of Dutch version of ASAQ item i
  score_English <- na.omit(data.frame(score=d0[,i ]))
  # Select scores of English version of ASAQ items i
  iccScore <- getLME(score_Dutch, score_English)
  l_ICC <- rbind(l_ICC, data.frame (i, icc = iccScore))
  # Calculated ICC and add it to the list of ICC values, 
  # with ID number of the ASA questionnaire item
}
l_ICC$Item = colnames(select(d0,HLA1:UAI4))
# give all items in the list the correct name
pander(l_ICC, caption = "ICC values for 90 items")
#display all ICC values on item-level

Variable <- c("Grand_mean","SD","Minimum","Maximum")
# Define the names of the statistics
Value <- c(round(mean(l_ICC$icc),digits=4),round(sd(l_ICC$icc),digits=4),
           round(min(l_ICC$icc),digits=4),round(max(l_ICC$icc),digits=4))
# Calculate the grand mean, standard deviation, minimum and maximum values of ICC values of 90 items
description <- cbind(Variable, Value) # Descriptive statistics of ICC values of 90 items

# Print results
pander(description, caption = "Descriptive statistics of ICC values of 90 items") 
```

For the assessment of the correlation between the English and Chinese ASA Questionnaire, we followed Cicchetti's classification of ICC categories. 
```{r, message=TRUE, warning=TRUE, echo=TRUE}
poor <- data.frame(ItemID = double(), Item = character(), icc = double())
fair <- data.frame(ItemID = double(), Item = character(), icc = double())
good <- data.frame(ItemID = double(), Item = character(), icc = double())
excellent <- data.frame(ItemID = double(), Item = character(), icc = double())
#Create categorizations of ICC values, ranging from poor to excellent

for(i in 1:90){
  if(l_ICC$icc[i]>=0.75) {
    #If the ICC value is greater than 0.75, it is excellent
     excellent <- rbind(excellent, data.frame (i ,l_ICC$Item[i] ,
                                               icc = l_ICC$icc[i]))
  } else if(l_ICC$icc[i]>=0.60) {
    #If the ICC value is between 0.60 and 0.75, it is good
     good <- rbind(good, data.frame (i, l_ICC$Item[i], icc = l_ICC$icc[i]))
  } else if(l_ICC$icc[i]>=0.4) {
    #If the ICC value is between 0.4 and 0.6, it is fair
     fair <- rbind(fair, data.frame (i, l_ICC$Item[i], icc = l_ICC$icc[i]))
  } else {
    #If the ICC value is below 0.4, it is poor
     poor <- rbind(poor, data.frame (i, l_ICC$Item[i], icc = l_ICC$icc[i]))
  }
}


pander(poor, caption = "ICC values for poor items")
pander(fair, caption = "ICC values for fair items")
pander(good, caption = "ICC values for good items")
pander(excellent, caption = "ICC values for excellent items")


#Display all ASA question items in their corresponding classification
```

## ICC values for 24 constructs and related dimensions
We first calculate the means of each construct/dimension and the we use in the same way as the item level ICC the LME function to calculate the ICC values for each construct. 

```{r, message=TRUE, warning=TRUE, echo=TRUE}
Dutch_column_offset <- length(d_total_Construct)/2

i <- which(names(d_total_Construct)%in%c("HLA1","HLB1","NA1","NB1","AAS1","AU1","PF1","AL1",
          "AS1","APP1","UAA1","R_AE1","UE1","UT1","UAL1","AA1","R_AC1","AI1","AT1",
          "SP1","IIS1","AEI1","UEP1","UAI1"))
#vector with the indexes of the first item of all constructs.

k <- c(ncol(select(d_total_Construct, HLA1:HLA4)),
       ncol(select(d_total_Construct, HLB1:HLB5)),
       ncol(select(d_total_Construct, NA1:NA5)),
       ncol(select(d_total_Construct, NB1:NB3)),
       ncol(select(d_total_Construct, AAS1:AAS3)),
       ncol(select(d_total_Construct, AU1:AU3)),
       ncol(select(d_total_Construct, PF1:PF3)),
       ncol(select(d_total_Construct, AL1:AL5)),
       ncol(select(d_total_Construct, AS1:AS3)),
       ncol(select(d_total_Construct, APP1:APP3)),
       ncol(select(d_total_Construct, UAA1:R_UAA3)),
       ncol(select(d_total_Construct, R_AE1:R_AE4)),
       ncol(select(d_total_Construct, UE1:UE3)),
       ncol(select(d_total_Construct, UT1:UT3)),
       ncol(select(d_total_Construct, UAL1:UAL6)),
       ncol(select(d_total_Construct, AA1:AA3)),
       ncol(select(d_total_Construct, R_AC1:R_AC4)),
       ncol(select(d_total_Construct, AI1:AI4)),
       ncol(select(d_total_Construct, AT1:R_AT3)),
       ncol(select(d_total_Construct, SP1:SP3)),
       ncol(select(d_total_Construct, IIS1:IIS4)),
       ncol(select(d_total_Construct, AEI1:R_AEI5)),
       ncol(select(d_total_Construct, UEP1:UEP4)),
       ncol(select(d_total_Construct, UAI1:UAI4)))
# 'k' is a vector with the  questionnaire items of each 
# construct/dimension

h <- cbind.data.frame(i,k) 
# Combine i and k into a data frame, whereby i indicates the column number 
# of the first English item of a construct and k the total number of adjacent 
# questionnaire items associated with the construct 

C_ICC <- data.frame(ConstructID=double(), Construct=character(), icc=double())  
# Initialize output of ICC values of 24 constructs/dimensions

for( p in 1:24 ) 
# Go step by step to 24 constructs/dimensions of the ASA questionnaire
{   
  i <- h[p,1] 
  # Column number of the first ASAQ item in English of the construct/dimension
  j <- i + Dutch_column_offset
  # The column number of the first ASAQ item in the 
  # Dutch version of the construct/dimension
  k <- h[p,2] 
  # The number of ASAQ items associate to the construct/dimension
  s_Dutch <- data.frame(d_total_Construct[,j:(j+k-1)]) 
  # Select the scores of all the ASAQ items in Dutch 
  # associated with the construct/dimension      
  s_English <- data.frame(d_total_Construct[,i:(i+k-1)]) 
  # Select the score of all the ASAQ items in English associated 
  # with the construct/dimension 
  average_s_Dutch <- data.frame(rowMeans(s_Dutch))
  # Calculate the mean score of ASAQ items in Dutch associated 
  # with the construct/dimension per participant
  average_s_English <- data.frame(rowMeans(s_English))  
  # Doing the same but now for English version of the items 
  colnames(average_s_Dutch) <- c("score") # Rename Dutch mean column      
  colnames(average_s_English) <- c("score") # Rename English mean column
  C_ICC <- rbind(C_ICC, data.frame (p, icc = getLME(average_s_Dutch, average_s_English)))
  # Call function 'getLME' for ICC value calculation
}

C_ICC$Construct = c('HLA','HLB','NA','NB','AAS','AU','PF','AL','AS','APP',
'UAA','AE','UE','UT','UAL','AA','AC','AI','AT','SP','IIS','AEI','UEP','UAI')
# Add construct/dimension name code
pander(C_ICC, caption = "ICC values for 24 constructs/dimensions")
# display the ICC values
```

The results are presented in the same way as the item-level ICC values.
```{r, message=FALSE, warning=FALSE, echo=TRUE}

Classification <- c("Excellent","Good","Fair","Poor") 
ICC_Range <- c("0.75-1.00","0.60-0.74","0.40-0.59","0-0.39")
# Categories of ICC classifications by Cicchetti (1994)
n_item <- length(C_ICC$icc) # Number of ICC values
round_ICC <- round(C_ICC$icc, digits=2) # Round ICC values
Number <- c(length(C_ICC[which(round_ICC>=0.75&round_ICC<=1),]$icc),
            length(C_ICC[which(round_ICC>=0.60&round_ICC<=0.74),]$icc),
            length(C_ICC[which(round_ICC>=0.40&round_ICC<=0.59),]$icc),
            length(C_ICC[which(round_ICC>=0.00&round_ICC<=0.39),]$icc))
# Calculate number of ICC values in classification category
Percentage <- c(round(Number[1]/n_item,digits=4)*100, round(Number[2]/n_item,digits=4)*100, 
                round(Number[3]/n_item,digits=4)*100, round(Number[4]/n_item,digits=4)*100)
# Calculate percentage of ICC values in classification category 
ICC_category <- cbind(Classification,ICC_Range,Number,Percentage)

# Print results
pander(ICC_category, caption = "Categories of ICC classifications and number 
       of ICC values in classification category for 24 constructs/dimensions") 

```
The grand mean, standard deviation and the range is also presented
```{r, message=FALSE, warning=FALSE, echo=TRUE}
Variable <- c("Grand_mean","SD","Minimum","Maximum")
# Define the names of the statistics
Value <- c(round(mean(C_ICC$icc),digits=4),round(sd(C_ICC$icc),digits=4),
           round(min(C_ICC$icc),digits=4),round(max(C_ICC$icc),digits=4))
# Calculate the grand mean, standard deviation, minimum and 
# maximum values of ICC values of 24 constructs/dimensions
description <- cbind(Variable, Value) 
# Descriptive statistics of ICC values of 24 constructs/dimensions

# Print results
pander(description, caption = "Descriptive statistics of ICC values 
of 24 constructs/dimensions") 
```

## ICC values between English and Chinese scores for the short version of ASA questionnaire
The last ICC calculation is for the ASAQ items of the short version of the ASAQ. The procedure is similar to ICC calculation of the 90 items, only this time, we select only the relevant 24 items first.

```{r, message=FALSE, warning=FALSE, echo=TRUE}
s_Dutch <- select(d_total_Item,D_HLA2,D_HLB5,D_NA4,D_NB3,D_AAS1,D_AU1,D_PF1,
                  D_AL2,D_AS1,D_APP1,D_UAA1, D_R_AE1,D_UE2,D_UT3,D_UAL1,D_AA2,
                  D_R_AC1,D_R_AI3,D_AT1,D_SP2,D_IIS2,D_R_AEI3,D_UEP3,D_UAI4)
# Select Chinese versions of the 24 representative ASAQ items
s_English <- select(d_total_Item,HLA2,HLB5,NA4,NB3,AAS1,AU1,PF1,AL2,AS1,APP1,
                    UAA1,R_AE1,UE2,UT3,UAL1,AA2,R_AC1,R_AI3,AT1,SP2,IIS2,R_AEI3,
                    UEP3,UAI4)
# Select English versions of the 24 representative ASAQ items
d_total_Short <- cbind(s_Dutch,s_English)
# Combine Chinese and English scores
n <- ncol(d_total_Short) # Numbers of all columns in d_total_Short
Dutch_column_offset <- n /2
s_ICC <- data.frame(ID=double(), Item=character(), icc=double())
# Initialize output of ICC values of 24 representative items
for (i in 1:24)
# Go step by step to 24 representative items of the ASA questionnaire
{
score_Dutch <- data.frame(score=d_total_Short[,i])
# Select Chinese scores of the ASAQ item
score_English <- data.frame(score=d_total_Short[,i+ Dutch_column_offset])
# Select English scores of the ASAQ item
s_ICC <- rbind(s_ICC, data.frame (i, icc = getLME(score_Dutch, score_English)))
# Call function 'getLME' for ICC value calculation
}
s_ICC$Item <- colnames(s_English) # Add item name code
pander(s_ICC, caption = "ICC values for 24 representative items")


Variable <- c("Grand_mean","SD","Minimum","Maximum")
# Define the names of the statistics
Value <- c(round(mean(s_ICC$icc),digits=4),round(sd(s_ICC$icc),digits=4),
           round(min(s_ICC$icc),digits=4),round(max(s_ICC$icc),digits=4))
# Calculate the grand mean, standard deviation, minimum 
# and maximum values of ICC values of 24 representative items
description <- cbind(Variable, Value) 
# Descriptive statistics of ICC values of 24 representative items

# Print results
pander(description, caption = "Descriptive statistics of ICC values 
of 24 representative items") 
```

```{r, message=FALSE, warning=FALSE, echo=TRUE}

Classification <- c("Excellent","Good","Fair","Poor") 
ICC_Range <- c("0.75-1.00","0.60-0.74","0.40-0.59","0-0.39")
# Categories of ICC classifications by Cicchetti (1994)
n_item <- length(s_ICC$icc) # Number of ICC values
round_ICC <- round(s_ICC$icc, digits=2) # Round ICC values
Number <- c(length(s_ICC[which(round_ICC>=0.75&round_ICC<=1),]$icc),
            length(s_ICC[which(round_ICC>=0.60&round_ICC<=0.74),]$icc),
            length(s_ICC[which(round_ICC>=0.40&round_ICC<=0.59),]$icc),
            length(s_ICC[which(round_ICC>=0.00&round_ICC<=0.39),]$icc))
# Calculate number of ICC values in classification category
Percentage <- c(round(Number[1]/n_item,digits=4)*100, round(Number[2]/n_item,digits=4)*100, 
                round(Number[3]/n_item,digits=4)*100, round(Number[4]/n_item,digits=4)*100)
# Calculate percentage of ICC values in classification category 
ICC_category <- cbind(Classification,ICC_Range,Number,Percentage)

# Print results
pander(ICC_category, caption = "Categories of ICC classifications and number 
       of ICC values in classification category for 24 representative items") 

```
